### 2013-12-06 manuscripts/reply/short-reply.tex
Working on `short-reply.tex`.
More edits throughout the ms.

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Biogeographers frequently seek to explain population and species
    differentiation on geographical phenomena.
    Establishing that a set of population splitting events occurred
    at the same time can be a potentially persuasive argument that a set of taxa
    are affected by the same geographic events.
    Unfortunately, estimating divergence times precisely when one lacks
    precise information about the rate of molecular evolution is a notoriously
    difficult problem in evolutionary biology.
    \citep{Huang2011} introduced an approximate Bayesian approach which can be
    used to estimate the probability of a model in which multiple sets of taxa
    diverge at the same time. 
    This method (implemented in the software \msb) does not require a common
    set of character data that links all of the taxa under investigation, but
    does require the relative mutation rates among the taxa and loci to be
    assumed a priori.
    Recently, \citet{Oaks2012} used this model-choice framework to 
    study 22 pairs of vertebrate lineages which are distributed across
    the Philippines; they also studied the behavior of the \msb approach
    using computer simulations.
    \citet{Oaks2012} found that the model was very sensitive to the 
    prior that is chosen and that the inference method had low power
    to detect variation in divergences times.
    These results were not surprising, in light of a rich statistical literature
    that shows that the marginal likelihood of a model is quite sensitive to the
    use of vague priors.
    Because this sensitivity to prior assumptions affects the crucial insights 
    that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
    that users of the approach should carefully assess the robustness of their 
    conclusions to different priors and the method's ability to detect
    temporal variation in divergences.
    According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
    was due to excessively broad priors on divergence times leading to 
    inadequate numbers of simulation replicates.
    They proposed a new model-averaging approach that uses narrow, empirically informed uniform
    priors.
    Here we demonstrate that the approach of \citet{Hickerson2013} is
    dangerous in the sense that the empirically-derived priors often
    exclude from consideration the true values of the models' parameters.
    On a more fundamental level, we question the value of adopting an 
    empirical Bayesian stance for this model-choice problem.
    The robust Bayesian approach of conducting analyses under a variety
    of priors can reveal prior sensitivity and communicate which assumptions
    underlie model inference.
    \vspace{12pt}
    \noindent\textbf{KEY WORDS: Approximate Bayesian computation; Bayesian
        model choice; empirical Bayes}

}

\newpage
\msb
\citep{Huang2011} uses approximate Bayesian computation (ABC) to
estimate the distribution of divergence times among co-distributed pairs of
taxa.
It approximates a posterior probability over models that range from a single
divergence-time parameter (i.e., simultaneous divergence of all pairs of taxa)
to the fully generalized model in which each pair of taxa diverged at a
unique time.
A full description of the model is given in \citet{Oaks2012}.
Frequently, the exact value of the divergence times are hard 
to determine because researchers typically lack precise knowledge 
of the rate at which substitutions occur.
So the exact divergence time is often viewed as a nuisance parameter, and
researchers focus on the number of divergence events.
The papers of \citet{Oaks2012} and \citet{Hickerson2013} are in agreement
on the fundamental methodological point about the model selection performed in \msb:
\begin{itemize}
   \item the use of vague priors on the divergence time parameters can 
    lead to support models with few divergence time events. Thus, the 
    primary inference enabled by the approach is very sensitive to the
    priors on divergence times.
\end{itemize}

\citet{Oaks2012} suggest the primary cause of the spurious support for models
with few divergence parameters is the greater marginal likelihoods of these
models under vague uniform priors relative to more parameter-rich models.
Models with more divergence-time parameters integrate over \emph{much} greater
parameter space with low probability of producing the data, yet relatively high
prior density \citep{Lindley1957} imposed by the uniformly distributed prior on
divergence times.
Note, this is a statistical issue extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.
\citet{Hickerson2013} suggest the bias is the result of a numerical issue
intrinsic to \msb, concluding the method's rejection algorithm is inefficient
and will be biased toward models with fewer divergence-time parameters, because
the parameter space of these models are more densely sampled relative to models
with more divergence-time parameters.
We agree that sampling error is present in all numerical Bayesian estimation
methods, however, we show here that it is not a major contributer to the
biases found by \citet{Oaks2012}.
We present results of additional analyses that, when combined with
the results of \citet{Oaks2012}, strongly suggest small marginal likelihoods of
models with more parameter space is a primary mechanism by which uniform priors
are causing \msb to prefer highly clustered models of divergences.

@@

% There are also differences between the papers regarding potential solutions to
% the bias.
\citet{Oaks2012} suggest alternative prior probability distributions on
divergence-times and other nuisance parameters could increase the marginal
likelihoods of models with more divergence-time parameters and thus reduce the
bias.
Alternatively, \citet{Hickerson2013} present an approach that uses empirically
informed uniform priors and Bayesian model-averaging in an attempt to accommodate
uncertainty in selecting priors.
% \citet{Hickerson2013} champion this strategy as a means of avoiding the
% pitfalls raised by \citet{Oaks2012}.
In general, we agree with the use of Bayesian model averaging to obtain a
posterior estimate marginalized over uncertainty in prior choice.
However, we question whether adding an additional dimension of model choice
that samples over empirically informed uniform priors is a fruitful solution
for a model-choice method that is very sensitive to priors.

In this paper, we discuss the potential theoretical and practical problems of
using empirically informed priors for Bayesian model choice.
Furthermore, we evaluate the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different multiple units of time, which makes the
results presented in their response difficult to interpret (see Supporting
Information for details).
Even when avoiding this error, we find Hickerson et al.'s
\citeyear{Hickerson2013} empirical Bayesian model-averaging implementation of
\msb remains biased toward clustered divergence models, and is predisposed to
excluding true parameter space.
The approach provides another means by which the method can ``escape'' models
with large parameter space, and the method's bias toward smaller models
remains.
Importantly, this bias can manifest in the preference of models that exclude
from consideration the true values of the model's parameters.
Our results, when combined with those of \citet{Oaks2012}, suggest that it is
difficult to choose a uniformly distributed prior on divergence times that is
broad enough to confidently contain the true values of parameters while being
narrow enough to avoid bias toward models with less parameter space.
However, recent work shows altnerative probability distributions without a
hard upper bound (e.g. gamma) can accomodate prior uncertainty in divergence
times while increasing the method's power to detect temporal variation in
divergences
\citet{Oaks2014dpp}.

% We discuss errors in this approach that render some of their results invalid
% and leave the remaining results difficult to interpret.
% Furthermore, we follow the recommendations of \citet{Oaks2012} and present
% simulation-based assessments of Hickerson et al.'s (\citeyear{Hickerson2013})
% approach.

% \cwlnote{}{This part seems important, but not related to the error in units
% discussed above}
% Another important characteristic of the approach used by \citet{Hickerson2013}
% that makes their results difficult to interpret is their use of narrow,
% empirically guided uniform priors in an approximate-Bayesian model-choice
% framework.
% We discuss the risks associated with this approach in the next section, and
% show how the results of \citet{Hickerson2013} likely exclude true values of the
% model's parameters.

% In addition to this error, we were not able to reproduce the results of
% \citet{Hickerson2013}.
% We followed their methods, generating $5\e6$ prior samples for each of the
% eight models in their Table 1.
% We retained the 10,000 samples from each model with the smallest Euclidean
% distance to the observed summary statistics, and subsequently retained 10,000
% samples from the remaining 80,000.

\section*{The potential implications of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} for divergence-time parameters as ``poorly selected.''
However, this is misleading, as \citet{Oaks2012} discuss in detail how they
selected their prior to reflect the large amount of uncertainty about the
timing of divergences across all 22 of the taxa in their study (see section
``Specifying and simulating the joint prior'' of \citet{Oaks2012}).
\citet{Oaks2012} further discuss how the use of uniform prior distributions in
\msb for many of the model's parameters requires investigators to select broad
priors to avoid excluding the truth \textit{a priori}, and how these broad
uniform priors place too much density in improbable regions of parameter space.

\citet{Hickerson2013} suggest that \citet{Oaks2012} should have used their
data to inform their prior on divergence times (i.e., an empirical Bayesian
approach).
However, \citet{Oaks2012} did use empirically informed priors to mimic
empirical situations in which a large amount of prior information is available;
they did so to assess the prior sensitivity of the method and to determine if
uniform priors in such situations are narrow enough to avoid the bias toward
models with few divergence-time parameters.
The results of \citet{Oaks2012} and \citet{Hickerson2013} showed the method is
highly sensitive to the prior on divergence times.
Furthermore, \citet{Oaks2012} found the method remained biased toward clustered
divergences even under the informed priors.

@@

To give the data more weight relative to the prior, we could use it twice, and
calculate an empirical Bayes estimate using a prior of $beta(13,17)$.  This
results in a ``posterior'' distribution of $beta(16, 24)$
(Figure~\ref{figCoinFlip}), with a MAP estimate of 0.395, and $p(M_1 \given
y=3, N=10) = 0.10$.
The estimated posterior distribution of the parameter, and resulting MAP
estimate, is similar whether or not an empirically informed prior is used.
However, the posterior probability of Model 1 is very sensitive to the
empirical prior, decreasing by 56\%.
By using the empirically informed prior, we ignored prior uncertainty, leading
to an underestimate of our posterior uncertainty (Figure~\ref{figCoinFlip}).
While this did not greatly affect our estimate of \myTheta{}, it did mislead us
toward overconfidence in Model 2.
% Our mode estimate of \myTheta{} under the empirical prior might be closer
% to the true value than our posterior mode.
% Let us assume the truth of the matter is that the coin under study has a broad
% flat edge, and as a result lands on its edge at a certain frequency.
% Hence, both of our models are incorrect (i.e., the outcomes of flipping the
% coin are not binomially distributed).

% Let us say that principal investigator Mary and her new postdoc Will are
% interested in the hypothesis that the mass of George Washington's periwig
% renders the quarter dollar of the United States unfair.
% That is to say their null hypothesis is that the probability of a US
% quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
% They can certainly evaluate this hypothesis, they can have undergraduate
% worker, Joe, flip the coin for them while they tabulate the results.
% But being Bayesians, before they call Joe into the lab, they agree on a
% prior probability to place on the set of all possible probabilities that
% the quarter will land heads when it is flipped.
% Given that neither of them have a quarter, and their prior knowledge that Joe
% moonlights as a magician, and is notorious for performing coin and card tricks
% in the lab, they suspect there is a good chance that the quarter Joe uses will
% be either two-headed or two-tailed.
% So, knowing that the beta distribution is the conjugate prior for a binomial
% likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
% (Figure~\ref{figCoinFlip}).

% %CWL:
% %I like the example, but it may be too cute. It is also too long. I think a
% %contrived example is good, but if there could be an example that is more
% %relevant to model choice and comparison of inaccurate posterior distributions,
% %I think that would be better. This is an example of empirical Bayes, but not
% %the potential problem with the use in msbayes. Unless I am interpreting wrong.
% %I would be careful about making it to cute as well. You may intend to make it
% %easy to understand for a general audience, but it can also seem like talking
% %down to Hickerson et al, who we are responding to. It just depends on how you
% %read it.
% This can be demonstrated with a simple, albeit contrived, example.
% Let us say that principal investigator Mary and her new postdoc Will are
% interested in the hypothesis that the mass of George Washington's periwig
% renders the quarter dollar of the United States unfair.
% That is to say their null hypothesis is that the probability of a US
% quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
% They can certainly evaluate this hypothesis, they can have undergraduate
% worker, Joe, flip the coin for them while they tabulate the results.
% But being Bayesians, before they call Joe into the lab, they agree on a
% prior probability to place on the set of all possible probabilities that
% the quarter will land heads when it is flipped.
% Given that neither of them have a quarter, and their prior knowledge that Joe
% moonlights as a magician, and is notorious for performing coin and card tricks
% in the lab, they suspect there is a good chance that the quarter Joe uses will
% be either two-headed or two-tailed.
% So, knowing that the beta distribution is the conjugate prior for a binomial
% likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
% (Figure~\ref{figCoinFlip}).

@@

% \cwlnote{}{It seems like this section can be boiled down to ``empirical Bayes
%     approaches for model choice when using uniform priors can exclude the
%     $truth$ from the prior, which is a violation of Bayes theorem" or something
%     like that. Picking apart what they calculated and we calculated seems like
%     too much detail. I would try to simplify how this is being presented. This
%     can lead into how the use of more appropriate prior distributions should be
%     used.}
In addition to the theoretical concerns discussed above, there are practical
problems with using narrow, empirically informed, uniform priors for a method
that has already been shown to be biased toward models with less parameter
space.
The results of Hickerson et al.'s \citeyear{Hickerson2013} reanalysis of the
Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This is concerning, because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa, a major problem when
using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior
density (HPD) interval for the mean divergence time estimated under one of the
priors used by \citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the limit on the prior, because
many of the taxon pairs are expected to have diverged at times older than the
upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).
The strong preference for the questionable priors on divergence times (their
$M_1$ and $M_2$) in the model-averaged results of \citet{Hickerson2013} suggest
their approach is biased toward models with less parameter space, and as a
consequence, is biased toward models that likely exclude the truth.
I.e., the approach is biased toward estimating model-averaged posteriors
dominated by models that exclude true values of parameters of the model.

%CWL:This should be in the section on model-averaging, not empirical Bayes
%limitations
We explored the propensity of the empirically informed model-averaging approach
of \citet{Hickerson2013} to exclude the truth in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging approach
of \citet{Hickerson2013}, but set one of prior models with a uniform prior on
divergence times that is unrealistically narrow, and almost certainly excludes
most, if not all, of the true divergence times of the 22 taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space, we expect \msb will preferentially sample from this
incorrect model yielding a marginal posterior that is incorrect (i.e., the
model-averaged posterior will be dominated by an incorrect model that excludes
the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

For our re-analysis of the Philippines dataset we followed the model-averaging
approach of \citet{Hickerson2013}, but with a reduced set of prior models to
avoid their error of mixing units of time (see SI for details).
We used five prior models, all of which had priors on population sizes of
$\meanDescendantTheta{} \sim U(0.0001, 0.1)$ and $\ancestralTheta{} \sim
U(0.0001, 0.05)$.
Following \citet{Hickerson2013}, each of these models had the following
priors on divergence time parameters:
$M_1$, $\divt{} \sim U(0, 0.1)$;
$M_2$, $\divt{} \sim U(0, 1)$;
$M_3$, $\divt{} \sim U(0, 5)$;
$M_4$, $\divt{} \sim U(0, 10)$; and
$M_5$, $\divt{} \sim U(0, 20)$.
We simulated $1\e6$ random samples from each of the models for a total of
$5\e6$ prior samples.
For each model, we retained the 10,000 samples with the smallest Euclidean
distance from the observed summary statistics, standardizing the statistics
using the prior means and standard deviations of the given model.
From the remaining 50,000 samples, we then retained the 10,000 samples with the
smallest Euclidean distance from the observed summary statistics, this time
standardizing the statistics using the prior means and standard deviations
across all five models.
We then repeated this analysis twice, replacing the $M_1$ model with
$M_{1A}$ and $M_{1B}$, which differ only by having priors on divergence
times of $\divt{} \sim U(0, 0.01)$ and $\divt{} \sim U(0, 0.001)$,
respectively.
While we suspect the prior of $\divt{} \sim U(0, 0.1)$ used by
\citet{Hickerson2013} likely excludes the true divergence times of at least
some of the 22 taxa, we are nearly certain that these narrower priors are
incorrect and exclude most, if not all, of the divergence times of the
Philippine taxa.

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the method's bias toward models with less parameter space,
but rather allows it to manifest in a concerning way.
The method strongly prefers the prior model with the narrowest distribution on
divergence times across all three of our analyses, even when this model is
almost certainly incorrect and excludes the true divergence times of the
Philippine taxa (Table~\ref{tabModelChoiceEmpirical}).

@@

To better quantify the propensity of Hickerson et al.'s
(\citeyear{Hickerson2013}) approach to exclude the truth, we simulated 1000
datasets in which the divergence times for the 22 population pairs are drawn
randomly from an exponential distribution with a mean of 0.5 ($\divt{} \sim
Exp(2)$).
All other parameters were identically distributed as the $M_1$--$M_5$ models
(Table~\ref{tabModelChoiceEmpirical}).
We then repeated the analysis described above using $1\e6$ random samples from
prior models $M_1$, $M_2$, $M_3$, $M_4$, and $M_5$, retaining 1000 posterior
samples for each of the 1000 simulated datasets.

>>>>

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Biogeographers frequently seek to explain population and species
    differentiation on geographical phenomena.
    Establishing that a set of population splitting events occurred
    at the same time can be a potentially persuasive argument that a set of taxa
    are affected by the same geographic events.
    Unfortunately, estimating divergence times precisely when one lacks
    precise information about the rate of molecular evolution is a notoriously
    difficult problem in evolutionary biology.
    \citep{Huang2011} introduced an approximate Bayesian approach which can be
    used to estimate the probabilities of models in which multiple sets of taxa
    diverge at the same time. 
    This method (implemented in the software \msb) does not require a common
    set of character data that links all of the taxa under investigation, but
    does require the relative mutation rates among the taxa and loci to be
    assumed \emph{a priori}.
    Recently, \citet{Oaks2012} used this model-choice framework to 
    study 22 pairs of vertebrate lineages which are distributed across
    the Philippines; they also studied the behavior of the \msb approach
    using computer simulations.
    \citet{Oaks2012} found that the model was very sensitive to the 
    prior that is chosen and that the inference method had low power
    to detect variation in divergences times.
    These results were not surprising, in light of a rich statistical literature
    that shows that the marginal likelihood of a model is quite sensitive to the
    use of vague priors.
    Because this sensitivity to prior assumptions affects the crucial insights 
    that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
    that users of the approach should carefully assess the robustness of their 
    conclusions to different priors.
    According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
    was due to excessively broad priors on divergence times leading to 
    inadequate numbers of simulation replicates.
    They proposed a new model-averaging approach that uses narrow, empirically informed uniform
    priors.
    Here we demonstrate that the approach of \citet{Hickerson2013} is
    dangerous in the sense that the empirically-derived priors often
    exclude from consideration the true values of the models' parameters.
    On a more fundamental level, we question the value of adopting an 
    empirical Bayesian stance for this model-choice problem.
    The robust Bayesian approach of conducting analyses under a variety
    of priors can reveal prior sensitivity and communicate which assumptions
    underlie model inference.
    Furthermore, simulations provide insight into the temporal resolution of
    the method, which in turn helps guide appropriate interpretation of
    results.

    \vspace{12pt}
    \noindent\textbf{KEY WORDS: Approximate Bayesian computation; Bayesian
        model choice; empirical Bayes} 
}

\newpage
\msb
\citep{Huang2011} uses approximate Bayesian computation (ABC) to
estimate the distribution of divergence times among co-distributed pairs of
taxa.
It approximates a posterior probability over models that range from a single
divergence-time parameter (i.e., simultaneous divergence of all pairs of taxa)
to the fully generalized model in which each pair of taxa diverged at a
unique time.
A full description of the model is given in \citet{Oaks2012}.
Frequently, the exact values of the divergence times are hard 
to determine because researchers typically lack precise knowledge 
of the rate at which substitutions occur.
So the exact divergence time is often viewed as a nuisance parameter, and
researchers focus on the number of divergence events.
The papers of \citet{Oaks2012} and \citet{Hickerson2013} are in agreement
on the fundamental methodological point about the model selection performed in \msb:
\begin{itemize}
   \item The use of vague priors on the divergence time parameters can lead to
       support models with few divergence events shared across taxa. Thus, the
       primary inference enabled by the approach is very sensitive to the
       priors on divergence times.
\end{itemize}

This is not surprising given the rich statistical literature that shows that
model marginal likelihoods are quite sensitive to the priors used in Bayesian
model selection
\citep[e.g.,][]{Jeffreys1935,Lindley1957}.
Accordingly, \citet{Oaks2012} suggest the primary cause of the spurious support
for models with few divergence parameters is the greater marginal likelihoods
of these models under vague uniform priors, relative to more parameter-rich
models.
Models with more divergence-time parameters integrate over \emph{much} greater
parameter space with low probability of producing the data, yet relatively high
prior density imposed by the uniformly distributed prior on divergence times.
Note, this is a statistical issue, extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.

\citet{Hickerson2013} suggest the bias is the result of a numerical issue
intrinsic to \msb, concluding the method's rejection algorithm is inefficient
and will be biased toward models with fewer divergence-time parameters, because
the parameter space of these models are more densely sampled relative to models
with more divergence-time parameters.
We agree that sampling error is present in all numerical Bayesian estimation
methods, however, we show here that it is not a major contributer to the
biases found by \citet{Oaks2012}.
We present results of additional analyses that, when combined with the results
of \citet{Oaks2012}, strongly suggest that \msb prefers models with few
divergence-time parameters, because they have greater likelihoods when
averaged over broad uniform priors on divergences times.

@@

% There are also differences between the papers regarding potential solutions to
% the bias.
\citet{Oaks2012} suggest alternative prior probability distributions on
divergence-times and other nuisance parameters could increase the marginal
likelihoods of models with more divergence-time parameters and thus reduce
spurious support for models of temporally clustered divergences.
Alternatively, \citet{Hickerson2013} present an approach that uses empirically
informed uniform priors and Bayesian model-averaging in an attempt to accommodate
uncertainty in selecting priors.
% \citet{Hickerson2013} champion this strategy as a means of avoiding the
% pitfalls raised by \citet{Oaks2012}.
In general, we agree with the use of Bayesian model averaging to obtain a
posterior estimate marginalized over uncertainty in prior choice.
However, we question whether adding an additional dimension of model choice
that samples over empirically informed uniform priors is a fruitful solution
for a model-choice method that is highly sensitive to priors.

In this paper, we discuss the potential theoretical and practical
considerations of using empirically informed priors for Bayesian model choice.
Furthermore, we evaluate the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different units of time, which makes the results
presented in their response difficult to interpret (see Supporting Information
for details).
Even when avoiding this error, we find their empirical Bayesian model-averaging
implementation of \msb remains biased toward clustered divergence models.
Furthermore, the approach provides another means by which the method can
``escape'' models with large parameter space, which manifests in the preference
of models that exclude from consideration the true values of the model's
parameters.
Our results, when combined with those of \citet{Oaks2012}, suggest that it is
difficult to choose a uniformly distributed prior on divergence times that is
broad enough to confidently contain the true values of parameters while being
narrow enough to avoid spurious support of models with less parameter space.
However, recent work shows more flexible probability distributions without a
hard upper bound (e.g., gamma) can accommodate prior uncertainty in divergence
times without inhibiting the marginal likelihoods of models with more
divergence-time parameters, and as a result, increase the method's power to
detect temporal variation in divergences
\citet{Oaks2014dpp}.

\section*{The potential implications of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} for divergence-time parameters as ``poorly selected.''
However, this is misleading, as \citet{Oaks2012} discuss in detail how they
selected their prior to reflect the large amount of uncertainty about the
timing of divergences across all 22 of the taxa in their study (see section
``Specifying and simulating the joint prior'' of \citet{Oaks2012}).
\citet{Oaks2012} further discuss how the use of uniform prior distributions in
\msb for many of the model's parameters requires investigators to select broad
priors to avoid excluding the truth \textit{a priori}, resulting in too much
density in improbable regions of parameter space.

\citet{Hickerson2013} suggest that \citet{Oaks2012} should have used their
data to inform their prior on divergence times (i.e., an empirical Bayesian
approach).
However, \citet{Oaks2012} did use empirically informed priors to mimic
empirical situations in which a large amount of prior information is available;
they did so to assess the prior sensitivity of the method and to determine if
uniform priors in such situations are narrow enough to avoid spurious support
of models with few divergence-time parameters.
The results of \citet{Oaks2012} and \citet{Hickerson2013} show the method is
highly sensitive to the prior on divergence times.
Furthermore, \citet{Oaks2012} found the method remained biased toward clustered
divergences under the informed priors.

@@

To give the data more weight relative to the prior, we could use it twice, and
calculate an empirical Bayes estimate using a prior of $beta(13,17)$.  This
results in a ``posterior'' distribution of $beta(16, 24)$
(Figure~\ref{figCoinFlip}), with a MAP estimate of 0.395, and $p(M_1 \given
y=3, N=10) = 0.10$.
The estimated posterior distribution of the parameter, and resulting MAP
estimate, is similar whether or not an empirically informed prior is used.
However, the posterior probability of Model 1 is very sensitive to the
empirical prior, decreasing by 56\%.
By using the empirically informed prior, we ignored prior uncertainty, leading
to an underestimate of our posterior uncertainty (Figure~\ref{figCoinFlip}).
While this did not greatly affect our estimate of \myTheta{}, it misled us
to be overconfident in Model 2.
% Our mode estimate of \myTheta{} under the empirical prior might be closer
% to the true value than our posterior mode.
% Let us assume the truth of the matter is that the coin under study has a broad
% flat edge, and as a result lands on its edge at a certain frequency.
% Hence, both of our models are incorrect (i.e., the outcomes of flipping the
% coin are not binomially distributed).

% This can be demonstrated with a simple, albeit contrived, example.
% Let us say that principal investigator Mary and her new postdoc Will are
% interested in the hypothesis that the mass of George Washington's periwig
% renders the quarter dollar of the United States unfair.
% That is to say their null hypothesis is that the probability of a US
% quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
% They can certainly evaluate this hypothesis, they can have undergraduate
% worker, Joe, flip the coin for them while they tabulate the results.
% But being Bayesians, before they call Joe into the lab, they agree on a
% prior probability to place on the set of all possible probabilities that
% the quarter will land heads when it is flipped.
% Given that neither of them have a quarter, and their prior knowledge that Joe
% moonlights as a magician, and is notorious for performing coin and card tricks
% in the lab, they suspect there is a good chance that the quarter Joe uses will
% be either two-headed or two-tailed.
% So, knowing that the beta distribution is the conjugate prior for a binomial
% likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
% (Figure~\ref{figCoinFlip}).

@@

% \cwlnote{}{It seems like this section can be boiled down to ``empirical Bayes
%     approaches for model choice when using uniform priors can exclude the
%     $truth$ from the prior, which is a violation of Bayes theorem" or something
%     like that. Picking apart what they calculated and we calculated seems like
%     too much detail. I would try to simplify how this is being presented. This
%     can lead into how the use of more appropriate prior distributions should be
%     used.}
In addition to the theoretical concerns discussed above, there are practical
problems with using narrow, empirically informed, uniform priors for a method
that has already been shown to be biased toward models with less parameter
space.
The results of Hickerson et al.'s \citeyear{Hickerson2013} reanalysis of the
Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This is concerning, because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa, a major problem when
using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior
density (HPD) interval for the mean divergence time estimated under one of the
priors used by \citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the limit on the prior, because
some of the taxon pairs are expected to have diverged at times older than the
upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).
The strong preference for the questionable priors on divergence times (their
$M_1$ and $M_2$) in the model-averaged results of \citet{Hickerson2013} suggest
their approach is biased toward models with less parameter space, and as a
consequence, is biased toward estimating model-averaged posteriors dominated by
models that exclude true values of parameters of the model.
We explored this possibility in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging approach
of \citet{Hickerson2013}, but set one of prior models with a uniform prior on
divergence times that is unrealistically narrow, and almost certainly excludes
most, if not all, of the true divergence times of the 22 taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space, we expect \msb will preferentially sample from this
incorrect model yielding a posterior that is incorrect (i.e., the
model-averaged posterior will be dominated by an incorrect model that excludes
the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

\subsubsection*{Re-analyses of the Philippines dataset using empirical Bayesian
model averaging}

For our re-analyses of the Philippines dataset we followed the model-averaging
approach of \citet{Hickerson2013}, but with a reduced set of prior models to
avoid their error of mixing units of time (see SI for details).
We used five prior models, all of which had priors on population sizes of
$\meanDescendantTheta{} \sim U(0.0001, 0.1)$ and $\ancestralTheta{} \sim
U(0.0001, 0.05)$.
Following \citet{Hickerson2013}, each of these models had the following
priors on divergence time parameters:
$M_1$, $\divt{} \sim U(0, 0.1)$;
$M_2$, $\divt{} \sim U(0, 1)$;
$M_3$, $\divt{} \sim U(0, 5)$;
$M_4$, $\divt{} \sim U(0, 10)$; and
$M_5$, $\divt{} \sim U(0, 20)$.
We simulated $1\e6$ random samples from each of the models for a total of
$5\e6$ prior samples.
For each model, we retained the 10,000 samples with the smallest Euclidean
distance from the observed summary statistics, standardizing the statistics
using the prior means and standard deviations of the given model.
From the remaining 50,000 samples, we then retained the 10,000 samples with the
smallest Euclidean distance from the observed summary statistics, this time
standardizing the statistics using the prior means and standard deviations
across all five models.
We then repeated this analysis twice, replacing the $M_1$ model with
$M_{1A}$ and $M_{1B}$, which differ only by having priors on divergence
times of $\divt{} \sim U(0, 0.01)$ and $\divt{} \sim U(0, 0.001)$,
respectively.
While we suspect the prior of $\divt{} \sim U(0, 0.1)$ used by
\citet{Hickerson2013} likely excludes the true divergence times of at least
some of the 22 taxa, we are nearly certain that these narrower priors are
incorrect and exclude most, if not all, of the divergence times of the
Philippine taxa.

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the method's support of models with less parameter space.
Rather, the method strongly prefers the prior model with the narrowest
distribution on divergence times across all three of our analyses, even when
this model is almost certainly incorrect and excludes the true divergence times
of the Philippine taxa (Table~\ref{tabModelChoiceEmpirical}).

@@

\subsubsection*{Simulation-based assessment of Hickerson et al.'s
\citeyear{Hickerson2013} model averaging over empirical priors}

To better quantify the propensity of Hickerson et al.'s
(\citeyear{Hickerson2013}) approach to exclude the truth, we simulated 1000
datasets in which the divergence times for the 22-population pairs are drawn
randomly from an exponential distribution with a mean of 0.5 ($\divt{} \sim
Exp(2)$).
All other parameters were identically distributed as the $M_1$--$M_5$ models
(Table~\ref{tabModelChoiceEmpirical}).
We then repeated the analysis described above using $1\e6$ random samples from
prior models $M_1$, $M_2$, $M_3$, $M_4$, and $M_5$, retaining 1000 posterior
samples for each of the 1000 simulated datasets.

For each simulation replicate, we estimated the Bayes factor in favor
of excluding the truth as the ratio of the posterior to prior odds of
excluding the true value of at least one parameter.
Whenever the Bayes factor preferred a model excluding the truth we counted the
number of the 22 true divergence times that were excluded by the preferred
model.
Our results show that the model-averaging approach of \citet{Hickerson2013}
favors a model that excludes the true values of parameters in 97\% of the
replicates (90\% with GLM-regression adjustment), excluding up to 21 of the 22
true divergence times (Figure~\ref{figExclusionSimTau}).
We also used the mode estimate of the preferred model for each replicate to
estimate the number of true parameter values excluded, which produced very
similar results.
Importantly, the posterior probability of excluding at least one true parameter
value is very high in nearly all of the replicates
(Figure~\ref{figExclusionSimProb}).
Using a Bayes factor of greater than 10 as a criterion for strong support, 66\%
of the replicates (87\% with GLM-regression adjustment) strongly support the
exclusion of true values (Figure~\ref{figExclusionSimProb}).

The results of the preceding empirical and simulation-based analyses clearly
demonstrate the risk of using narrow, empirically guided uniform priors in a
Bayesian model-averaging framework.
The consequence of this approach is obtaining a model-averaged posterior
estimate that is heavily weighted toward incorrect models that exclude true
values of model parameters.

\subsection*{Additional thoughts on empirical priors in Bayesian model choice}
The preceding sections are not a general critique of Bayesian model averaging.
Rather, model averaging can provide an elegant way of incorporating
model uncertainty in Bayesian inference.
However, when averaging over models with narrow and broad uniform priors in
situations where the likelihood density is not expected to be uniformly
distributed, the posterior could be dominated by models that exclude from
consideration the true values of parameters due to the larger marginal
likelihoods of the models that are integrated over less space with high prior
weight yet low likelihood.
